Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-08-20 paper/v2.0/sections/1_introduction.tex
Grammer corrections

Manipulating light-matter interactions in the quantum regime paved the path for an astonishing number of useful technologies in the last century. Quantum optics, which study these interactions, have drawn research attention to the disciplines of optoelectronics \cite{liu16,wijesekara20,tao21,wijesekara21}, sensing \cite{rodrigo15,pirandola18,hapuarachchi2018}, energy harvesting \cite{weeraddana15,yuan16,sun18},
quantum computing \cite{huh15,slussarenko19,andersen21}, bio-information \cite{marais18,bian20}, and many other specialities of recent technologies \cite{rivera20}.
The studies on quantum optics of nanostructures were generally centered on metamaterials \cite{shalaev07,si14}, quantum plasmonic effects \cite{hapuarachchi19,perera20}, lasers and amplifiers \cite{chow13,jayasekara16,premaratne17}, and quantum cavity physics \cite{tsang10,liu17,devi20}.
However, in recent years, one of the foremost aim of examining nanostructures under external radiation was understanding their electron transport characteristics \cite{kitagawa11,zhou11,kibis14,pervishko15,morina15,dehghani15,dini16,wackerl20}.

@@

Theoretical analyses on the transport properties of dressed fermion systems were recently reported in Refs. \cite{kibis14,morina15,wackerl20}.
Furthermore, in Ref. \cite{wackerl20} a general expression for conductivity in a dressed system has been derived in a fully closed analytical form. In their study, a novel type of Green’s functions, namely four-times Green’s functions were used to derive the Floquet-Drude conductivity formula. This opened the path to exploring and exploiting nanostructures' charge transport attributes under an intense dressing field.

@@

In the present analysis, we present a robust mathematical model for a dressed two-dimensional electron gas (2DEG) subject to another nonoscillating magnetic field.
A stationary magnetic field is applied perpendicularly across the surface of the 2DEG system. This causes the orbital motion of the electrons to be quantized, and a discrete energy spectrum with Landau splitting is observed \cite{landau30}.
In this study, we explicitly calculate the longitudinal components ($\sigma^{xx},\sigma^{yy}$) of the conductivity tensor in a periodically driven quantum Hall system by developing a generalized analytical description using the Floquet-Drude conductivity \cite{wackerl20}.
Finally, we demonstrate that our generalized model reproduces the results of the state-of-the-art conductivity model in Ref. \cite{endo09}, which was developed for the more specific case of quantum Hall systems without the external dressing field.
Moreover, we find that the optical field can be used as a mechanism to regulate transport behavior in numerous 2D nanostructures which can serve as a basis for many useful nanoelectronic devices. We believe that our theoretical analysis and visual depictions of numerical results will lead to a better understanding of manipulating charge transport. Moreover, this will inspire advanced  developments in nanoscale quantum devices.

>>>>

Manipulating light-matter interactions in the quantum regime paved the path for an astonishing number of useful technologies in the last century. Quantum optics, which study these interactions, have drawn research attention to the disciplines of optoelectronics \cite{liu16,wijesekara20,tao21,wijesekara21}, sensing \cite{rodrigo15,pirandola18,hapuarachchi2018}, energy harvesting \cite{weeraddana15,yuan16,sun18},
quantum computing \cite{huh15,slussarenko19,andersen21}, bio-information \cite{marais18,bian20}, and many other specialities of recent technologies \cite{rivera20}.
The studies on quantum optics of nanostructures were generally centered on metamaterials \cite{shalaev07,si14}, quantum plasmonic effects \cite{hapuarachchi19,perera20}, lasers and amplifiers \cite{chow13,jayasekara16,premaratne17}, and quantum cavity physics \cite{tsang10,liu17,devi20}.
However, in recent years, one of the foremost aims of examining nanostructures under external radiation was understanding their electron transport characteristics \cite{kitagawa11,zhou11,kibis14,pervishko15,morina15,dehghani15,dini16,wackerl20}.

@@

Theoretical analyses on the transport properties of dressed fermion systems were recently reported in Refs. \cite{kibis14,morina15,wackerl20}.
Furthermore, in Ref. \cite{wackerl20} a general expression for conductivity in a dressed system has been derived in a fully closed analytical form. In their study, a novel type of Green’s functions, namely four-times Green’s functions were used to derive the Floquet-Drude conductivity formula. This opened the path for exploring and exploiting nanostructures' charge transport attributes under an intense dressing field.

@@

In the present analysis, we introduce a robust mathematical model for a dressed two-dimensional electron gas (2DEG) subject to another nonoscillating magnetic field.
A stationary magnetic field is applied perpendicularly across the surface of the 2DEG system. This causes the orbital motion of the electrons to be quantized, and a discrete energy spectrum with Landau splitting is observed \cite{landau30}.
In this study, we explicitly calculate the longitudinal components ($\sigma^{xx},\sigma^{yy}$) of the conductivity tensor in a periodically driven quantum Hall system by developing a generalized analytical description using the Floquet-Drude conductivity \cite{wackerl20}.
Finally, we demonstrate that our generalized model reproduces the results of the state-of-the-art conductivity model in Ref. \cite{endo09}, which was developed for the more specific case of quantum Hall systems without the external dressing field.
Moreover, we find that the optical field can be used as a mechanism to regulate transport behavior in numerous 2D nanostructures which can serve as a basis for many useful nanoelectronic devices. We believe that our theoretical analysis and visual depictions of numerical results will lead to a better understanding of manipulating charge transport. Moreover, this will inspire advanced  developments in nanoscale quantum devices.

### 2021-08-20 paper/v2.0/sections/3_floquet_theory.tex
Grammer corrections

Symmetry conditions often give useful insights into the behaviors of physical quantum systems.
For instance, in the famous Bloch analysis of electrons in quantum systems introduces a mathematical explanation for quantum systems occupying a discrete translational symmetry in the configuration space. Similarly, Floquet theory gives a mathematical formalism that can be used for translational symmetry in time rather than in space \cite{floquet83,grifoni98,holthaus15}.
The Floquet-Drude conductivity theory was employed recently by Wackerl \textit{et al.} \cite{wackerl20} as a method to analyze the transport properties of quantum systems exposed to strong radiation.
In their work, they have presented more accurate results than the former theoretical descriptions for the conductivity of nanoscale systems in the  presence of a dressing field. Therefore, we apply the Floquet-Drude conductivity theory to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.

>>>>

Symmetry conditions often give useful insights into the behaviors of physical quantum systems.
For instance, the famous Bloch analysis of electrons in quantum systems introduces a mathematical explanation for quantum systems occupying a discrete translational symmetry in the configuration space. Similarly, Floquet theory gives a mathematical formalism that can be used for translational symmetry in time rather than in space \cite{floquet83,grifoni98,holthaus15}.
The Floquet-Drude conductivity theory was employed recently by Wackerl \textit{et al.} \cite{wackerl20} as a method to analyze the transport properties of quantum systems exposed to strong radiation.
In their work, they have presented more accurate results than the former theoretical descriptions for the conductivity of nanoscale systems in the  presence of a dressing field. Therefore, we apply the Floquet-Drude conductivity theory to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.
